# The structure of the codes {#structure}

In this chapter, we list the structure of the code for the project.
Codes are categorized in the following categories by their usage:
1. data creation
2. analysis
  1. data cleaning/manipulation
  2. data merge
  3. estimations
  4. counterfactual analysis
3. table and figure knitting
  1. summary statistics
  2. regressions
  3. histograms and other figures

The following sections display the tree diagrams of the scripts, and show the dependencies of each script. Note that a `.R` file indicates a single script, and some features may require more than one script to realize. 


```{bash, eval=FALSE}
D:.
├───analysis
├───create_data
│   └───old
├───drafts
│   ├───figures
│   │   ├───old
│   │   ├───old - delete
│   │   └───test
│   └───tables
│       ├───old
│       ├───old - delete
│       └───test
├───knit_tables
│   └───old
└───Koijen Yogo
    ├───Data
    │   ├───Compustat
    │   │   └───2017
    │   ├───CRSP
    │   │   └───2017
    │   ├───Fama French
    │   │   ├───Fama-French Factors
    │   │   └───Industry Definitions
    │   │       └───Stata
    │   ├───SEC
    │   │   └───Form ADV
    │   │       └───Registered
    │   │           └───Stata
    │   ├───Thomson Reuters
    │   │   ├───13F
    │   │   │   ├───2016
    │   │   │   └───2017
    │   │   └───Ownership
    │   │       └───2017
    │   └───WRDS-SEC
    └───Programs
        ├───Data
        │   ├───Compustat
        │   │   └───2017
        │   ├───CRSP
        │   │   └───2017
        │   ├───Fama French
        │   │   ├───Fama-French Factors
        │   │   └───Industry Definitions
        │   │       └───Stata
        │   ├───SEC
        │   │   └───Form ADV
        │   │       └───Registered
        │   │           └───Stata
        │   ├───Thomson Reuters
        │   │   ├───13F
        │   │   │   ├───2016
        │   │   │   └───2017
        │   │   └───Ownership
        │   │       └───2017
        │   └───WRDS-SEC
        ├───Matlab
        └───Stata
            ├───Construction
            │   └───Modified
            ├───Data
            │   ├───2
            │   ├───3
            │   ├───Bins_csv
            │   └───Jin_0925
            ├───Decomposition
            ├───Estimation
            ├───Institutions
            ├───Liquidity
            └───Predictability

```



## Data Creation {-}

```{r}
fs::dir_tree(paste0(project_path, "create_data"), 
             recurse = TRUE, 
             # regexp = "*.r"
             )
```

## Analysis {-}
```{r}
fs::dir_tree(paste0(project_path, "analysis"), 
             recurse = TRUE, 
             # regexp = "*.r"
             )
```
TBA

## Knitting {-}
```{r}
fs::dir_tree(paste0(project_path, "knit_tables"), 
             recurse = TRUE, 
             # regexp = "*.r"
             )
```
TBA

